NumPy---Array Programming in Python

### 2020-01-11 body.tex
Minor edits

Other utility functions include creating, reshaping, concatenating, and padding
arrays; searching, sorting and counting data; and reading and writing files.
NumPy provides extensive support for generating pseudorandom numbers and
includes an assortment of probability distributions.
It also performs accelerated linear algebra, utilising one of several backends
such as OpenBLAS and Intel MKL optimized for the CPUs at hand.

@@

- massive explosion in data science, machine learning, and artificial intelligence (tensors)

>>>>

Other utility functions include creating, reshaping, concatenating, and padding
arrays; searching, sorting and counting data; and reading and writing files.
NumPy provides extensive support for generating pseudorandom numbers and
includes an assortment of probability distributions.
It also performs accelerated linear algebra, utilizing one of several backends
such as OpenBLAS and Intel MKL optimized for the CPUs at hand.

@@

- massive explosion in data science, machine learning, and artificial intelligence

### 2020-01-11 summary.tex
Minor edits

% - 2-3 sentences of basic-level introduction to the field;
Array programming provides powerful notation for accessing,
manipulating, and operating on data in vectors, matrices, and
higher-dimensional arrays \cite{iverson1980notation}.
% - a brief account of the background and rationale of the work;
NumPy is the fundamental array programming library for the Python programming language
\cite{dubois2007guest,oliphant2007python,millman2011python,perez2011python}.
It has been actively developed for over two decades and has more than 850
contributors, nearly 300,000 dependent repositories on GitHub, and millions of
downloads per year.
It plays an essential role in research analysis pipelines in fields as
diverse as physics, biology, astronomy, neuroscience, material science,
engineering, and chemistry.
For example, in astronomy, NumPy was fundamental to discovering gravitational
waves\cite{pycbc}, the first imaging of a black hole\cite{eht-imaging}, and
continues underpinning the future exploration of our
universe\cite{jenness2018lsst}.
It is one of the most commonly used machine learning tools among
enterprises \cite{451report2018}.
% - a statement of the main conclusions (introduced by the phrase 'Here we show' or its equivalent);
Here we show how a few core ideas lead to a simple and powerful array syntax.
% - 2-3 sentences putting the main findings into general context so it is
%   clear how the results described in the paper have moved the field forwards.
NumPy arrays are so popular that several project have developed their own
NumPy-like interface and array objects targeting audiences with specialized
needs.
Because of this, NumPy plays a unique role in enabling disparate technologies
to interact and exchange.
%NumPy continues to evolve to meet the needs of its community, to remain
%relevant in an ever-changing computing landscape, and to be a fundamental
%pillar of support for the next decade of scientific computing, data science,
%and machine learning in Python.

>>>>

% - 2-3 sentences of basic-level introduction to the field;
Array programming provides powerful notation for accessing,
manipulating, and operating on data in vectors, matrices, and
higher-dimensional arrays \cite{iverson1980notation}.
% - a brief account of the background and rationale of the work;
NumPy is the fundamental array programming library for the Python language
\cite{dubois2007guest,oliphant2007python,millman2011python,perez2011python}.
It has been actively developed for over two decades and has more than 850
contributors, nearly 300,000 dependent repositories on GitHub, and millions of
downloads per year.
It plays an essential role in research analysis pipelines in fields as
diverse as physics, biology, astronomy, neuroscience, material science,
engineering, and chemistry.
For example, in astronomy, NumPy was fundamental to discovering gravitational
waves\cite{pycbc}, the first imaging of a black hole\cite{eht-imaging}, and
continues underpinning the future exploration of our
universe\cite{jenness2018lsst}.
It is one of the most commonly used machine learning tools among
enterprises \cite{451report2018}.
% - a statement of the main conclusions (introduced by the phrase 'Here we show' or its equivalent);
Here we show how a few fundamental concepts lead to a simple and powerful array syntax.
% - 2-3 sentences putting the main findings into general context so it is
%   clear how the results described in the paper have moved the field forwards.
NumPy is so popular that several project have developed their own
NumPy-like interface and array objects targeting audiences with specialized
needs.
Because of this, NumPy plays a unique role in enabling disparate technologies
to interact and exchange data.
%NumPy continues to evolve to meet the needs of its community, to remain
%relevant in an ever-changing computing landscape, and to be a fundamental
%pillar of support for the next decade of scientific computing, data science,
%and machine learning in Python.
